---
title: "Unit 1 - 3 Review Starter"
author: "Genesis - Claudia, Mya, Sofia, Sydney, Caroline"
date: "2023-03-09"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand_minerals.csv")
location_descriptions <- read_csv("data/location_descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility_hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sites)
variable.names(sites)
```

There are `r nrow(sites)` rows and `r ncol(sites)` variables. Each row shows a different site location, numbered 1 through 10, and which sand mineral was found at that site. The variable names are "location" and "minerals."

### Exercise 2

```{r inspect-other-dataframes}
glimpse(density)
glimpse(solubility_hardness)
glimpse(location_descriptions)
variable.names(density)
variable.names(solubility_hardness)
variable.names(location_descriptions)
```

There are `r nrow(density)` rows and `r ncol(density)` variables in the density data frame. Each row shows the density of the three types of sand minerals. The variable names are "minerals" and "density."

There are `r nrow(solubility_hardness)` rows and `r ncol(solubility_hardness)` variables in the solubility_hardness data frame. Each row shows the solubility and hardness of the three types of sand minerals. The variable names are "minerals", "solubility" and "hardness."

There are `r nrow(location_descriptions)` rows and `r ncol(location_descriptions)` variables in the location_descriptions data frame. Each row shows a different location, 1 through 10, and a description of that location. The variable names are "location" and "loc_desc."

### Exercise 3

```{r join-mineral-properties}
sand_mineral_density <- sites %>%
  left_join(density)
sand_mineral_properties <- sand_mineral_density %>%
  left_join(solubility_hardness)
```

There are `r nrow(sand_mineral_density)` rows in the new data frame. This is the same number of rows as the original sand minerals data frame. 

### Exercise 4

```{r sand-grains-observed}
count(sand_mineral_properties, location)
```
```{r slice}
slice(sand_mineral_properties, 14:23)
```

```{r arrange}
sand_mineral_properties %>%
  arrange(desc(density)) %>%
  slice(14:23)
```
```{r location-hardness}
sand_mineral_properties %>%
  select(one_of(c("location", "hardness"))) %>%
  slice(19:23)
```
```{r remove-NAs}
sand_mineral_properties %>%
  na.omit(hardness) %>%
  arrange(desc(density)) %>%
  slice(5:14)
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

## Part II - Data Visualization

`starwars` is already loaded within the `dplyr` package (within `tidyverse`)

### Exercise 7

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 8

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 9

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
